Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-04-08 paper.tex
Shrink some hboxes
Redraw another picture

\usetikzlibrary{shapes, shapes.multipart, arrows, positioning}

@@

\begin{figure}[tb]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{oriented.pdf}
\caption{A pictorial representation of the orientation process, stage 4. Top right is the actual
oriented schedule. Below that is the DFA to satisfy criterion~5. On the left is the zero/one
variables, a row representing a skippers sequence of competitors. An edge between variables
corresponds to a matched pair, that must take different values. Bottom right is a sketch by third
author.}\label{oriented}
\end{figure}

@@

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.5\textwidth}
    \centering
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (5,2) & (4,3) & (1,6) \\
        1 & (4,2)  & (6,5) & (3,1) \\
        2 & (6,4) & (2,1) & (3,5) \\
        3 & (6,2) & (5,0) & (1,7) \\
        4 & (5,1) & (0,6) & (2,7) \\
        5 & (7,5) & (2,0) & (6,3) \\
        6 & (0,7) & (4,1) & (3,2) \\
       7 & (7,4)  & (0,3) &  \\
       8 & (4,0)  & (7,3) &  \\
       9 & (5,4)  & (7,6) & (1,0) \\ \bottomrule
    \end{tabular}
\label{08-06a}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
    \centering
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (2,7) & (3,0) & (5,4) \\
        1 & (0,2)  & (4,3) & (7,5) \\
        2 & (0,4) & (7,6) & (5,3) \\
        3 & (4,6) & (5,0) & (3,1) \\
        4 & (6,5) & (3,2) & (1,4) \\
        5 & (6,3) & (4,7) & (2,1) \\
        6 & (7,3) & (1,6) & (4,2) \\
       7 & (7,1)  & (2,5) & (6,0) \\
       8 & (5,1)  & (0,7) & (6,2) \\
       9 & (1,0)  & & \\ \bottomrule
    \end{tabular}
\label{08-06b}
\end{minipage}
\caption{Schedules for 8 skippers and 6 boats. On the left, the published ISAF schedule (illegal),
and on the right is our schedule.}
\label{08-06}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.5\textwidth}
\centering
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (0,7) & (3,2) & (5,4) \\
        1 & (0,2) & (7,4) & (5,3) \\
        2 & (4,0) & (7,3) & (2,5) \\
        3 & (3,0) & (2,4) & (6,5) \\
        4 & (4,3) & (5,1) & (8,6) \\
        5 & (3,1) & (6,2) & (4,8) \\
        6 & (6,3) & (1,4) & (8,2) \\
        7 & (4,6) & (2,7) & (1,8) \\
        8 & (7,6) & (0,8) & (2,1) \\
        9 & (8,7) & (5,0) & (6,1) \\
        10 & (8,5) & (1,7) & (0,6) \\
        11 & (7,5) & (3,8) & (1,0) \\ \bottomrule
    \end{tabular}
\centering
\label{09-06}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\begin{tabular}{ccccc}
        \toprule
        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
        0 & (0,6) & (3,2) & (5,4) & (1,7) \\
        1 & (2,0) & (6,3) & (4,1) & (8,7) \\
        2 & (6,4) & (0,5) & (7,2) & (3,8) \\
        3 & (4,7) & (1,8) & (0,3) & (5,2) \\
        4 & (3,1) & (7,5) & (8,0) & (2,6) \\
        5 & (3,7) & (4,8) & (2,1) & (6,5) \\
        6 & (8,2) & (1,6) & (5,3) & (0,4) \\
        7 & (5,1) & (7,0) & (6,8) & (4,3) \\
        8 & (8,5) & (2,4) & (7,6) & (1,0) \\ \bottomrule
        & & & & \\
        & & & & \\
        & & & & \\
    \end{tabular}
\label{09-08}
\end{minipage}
\caption{Two new schedules. On the left, 9 skippers and 6 boats, and on the right 9 skippers and 8 boats.}
\label{09}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.5\textwidth}
    \centering
\begin{tabular}{cccc}
 \toprule
Flight & \multicolumn{3}{c}{Matches} \\ \midrule
0 & (8,3) &  (1,7) &  (0,9) \\
1 & (7,3) &  (0,8) &  (1,9) \\
2 & (0,7) &  (9,3) &  (1,8) \\
3 & (6,2) &  (5,0) &  (7,4) \\
4 & (5,2) &  (6,4) &  (3,0) \\
5 & (8,6) &  (2,9) &  (4,1) \\
6 & (7,2) &  (4,8) &  (9,6) \\
7 & (2,4) &  (0,6) &  (7,5) \\
8 & (6,1) &  (5,9) &  (8,2) \\
9 & (9,4) &  (8,7) &  (6,5) \\
10 & (9,7) &  (6,3) &  (8,5) \\
11 & (7,6) &  (3,1) &  (9,8) \\
12 & (4,3) &  (5,1) &  (2,0) \\
13 & (3,5) &  (4,0) &  (2,1) \\
14 & (5,4) &  (3,2) &  (1,0) \\ \bottomrule
\end{tabular}
\label{10-06a}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\begin{tabular}{ccccc}
\toprule
Flight & \multicolumn{3}{c}{Matches} \\ \midrule
0 & (4,7) & (3,2) & (0,5) \\
1 & (2,4) & (7,0) & (3,5) \\
2 & (0,4) & (7,3) & (5,2) \\
3 & (4,3) & (0,2) & (5,7) \\
4 & (3,0) & (6,5) & (2,7) \\
5 & (6,3) & (7,1) & (8,2) \\
6 & (7,6) & (2,1) & (9,8) \\
7 & (2,6) & (8,7) & (4,9) \\
8 & (6,8) & (1,4) & (7,9) \\
9 & (8,1) & (5,4) & (9,6) \\
10 & (5,1) & (9,2) & (4,6) \\
11 & (1,9) & (6,0) & (8,4) \\
12 & (0,9) & (3,8) & (6,1) \\
13 & (8,0) & (9,5) & (1,3) \\
14 & (5,8) & (9,3) & (1,0) \\ \bottomrule
\end{tabular}
\label{10-06b}
\end{minipage}
\caption{Schedules for 10 skippers and 6 boats. On the left, the ISAF published schedule (illegal),
and on the right, our schedule.}
\label{10-06}
\end{figure}
\end{center}

>>>>

\usetikzlibrary{shapes, shapes.multipart, arrows, positioning, calc}

@@

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}
        \begin{scope}[every node/.style={minimum size=2em,inner sep=1}]
            \node (R0N)                                                at (0.4,  0) { 0: };
            \node (R00) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 1,  0)$) { 6 };
            \node (R01) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 2,  0)$) { 2 };
            \node (R02) [draw, circle, fill=uofglawn]                  at ($(1.2 * 3,  0)$) { 5 };
            \node (R03) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4,  0)$) { 3 };
            \node (R04) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 5,  0)$) { 4 };
            \node (R05) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 6,  0)$) { 1 };

            \node (R1N)                                                at (0.4, -1) { 1: };
            \node (R10) [draw, circle, fill=uofglawn]                  at ($(1.2 * 1, -1)$) { 4 };
            \node (R11) [draw, circle, fill=uofglawn]                  at ($(1.2 * 2, -1)$) { 2 };
            \node (R12) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -1)$) { 5 };
            \node (R13) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4, -1)$) { 6 };
            \node (R14) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 5, -1)$) { 3 };
            \node (R15) [draw, circle, fill=uofglawn]                  at ($(1.2 * 6, -1)$) { 0 };

            \node (R2N)                                                at (0.4, -2) { 2: };
            \node (R20) [draw, circle, fill=uofglawn]                  at ($(1.2 * 1, -2)$) { 3 };
            \node (R21) [draw, circle, fill=uofglawn]                  at ($(1.2 * 2, -2)$) { 0 };
            \node (R22) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -2)$) { 1 };
            \node (R23) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 4, -2)$) { 4 };
            \node (R24) [draw, circle, fill=uofglawn]                  at ($(1.2 * 5, -2)$) { 5 };
            \node (R25) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 6, -2)$) { 6 };

            \node (R3N)                                                at (0.4, -3) { 3: };
            \node (R30) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 1, -3)$) { 2 };
            \node (R31) [draw, circle, fill=uofglawn]                  at ($(1.2 * 2, -3)$) { 6 };
            \node (R32) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -3)$) { 0 };
            \node (R33) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 4, -3)$) { 5 };
            \node (R34) [draw, circle, fill=uofglawn]                  at ($(1.2 * 5, -3)$) { 1 };
            \node (R35) [draw, circle, fill=uofglawn]                  at ($(1.2 * 6, -3)$) { 4 };

            \node (R4N)                                                at (0.4, -4) { 4: };
            \node (R40) [draw, circle, fill=uofglawn]                  at ($(1.2 * 1, -4)$) { 5 };
            \node (R41) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 2, -4)$) { 1 };
            \node (R42) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -4)$) { 6 };
            \node (R43) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4, -4)$) { 2 };
            \node (R44) [draw, circle, fill=uofglawn]                  at ($(1.2 * 5, -4)$) { 0 };
            \node (R45) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 6, -4)$) { 3 };

            \node (R5N)                                                at (0.4, -5) { 5: };
            \node (R50) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 1, -5)$) { 4 };
            \node (R51) [draw, circle, fill=uofglawn]                  at ($(1.2 * 2, -5)$) { 6 };
            \node (R52) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -5)$) { 0 };
            \node (R53) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4, -5)$) { 1 };
            \node (R54) [draw, circle, fill=uofglawn]                  at ($(1.2 * 5, -5)$) { 3 };
            \node (R55) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 6, -5)$) { 2 };

            \node (R6N)                                                at (0.4, -6) { 6: };
            \node (R60) [draw, circle, fill=uofglawn]                  at ($(1.2 * 1, -6)$) { 0 };
            \node (R61) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 2, -6)$) { 5 };
            \node (R62) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -6)$) { 3 };
            \node (R63) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4, -6)$) { 4 };
            \node (R64) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 5, -6)$) { 1 };
            \node (R65) [draw, circle, fill=uofglawn]                  at ($(1.2 * 6, -6)$) { 2 };

            \draw [thick] (R00) to [out=300, in=90] ($(R30) + (0.6, 0)$) to [out=270, in=60] (R60);
            \draw [thick] (R10) to [out=300, in=120] (R41);
            \draw [thick] (R20) to                   (R30);
            \draw [thick] (R40) to                   (R50);

            \draw [thick] (R01) to [out=230, in=130] (R21);
            \draw [thick] (R11) to                   (R22);
            \draw [thick] (R31) to [out=300, in=120] (R62);
            \draw [thick] (R51) to                   (R61);

            \draw [thick] (R02) to [out=245, in=115] (R52);
            \draw [thick] (R12) to [out=300, in=120] (R53);
            \draw [thick] (R32) to [out=45,  in=225] (R03);
            \draw [thick] (R42) to                   (R63);

            \draw [thick] (R13) to [out=300, in=120] (R64);
            \draw [thick] (R23) to [out=230, in=130] (R43);
            \draw [thick] (R33) to                   (R54);

            \draw [thick] (R04) to [out=245, in=115] (R44);
            \draw [thick] (R14) to [out=310, in=50]  (R34);
            \draw [thick] (R24) to [out=300, in=120] (R55);

            \draw [thick] (R05) to                   (R15);
            \draw [thick] (R25) to [out=245, in=115] (R65);
            \draw [thick] (R35) to                   (R45);
        \end{scope}

        \begin{scope}[every node/.style={minimum size=2em,inner sep=1}, xshift=8.7cm, yshift=-5cm]
            \node (DFAI)  [draw, circle, fill=white]                     at (0,  0)   { \phantom{$P_1$} };
            \node (DFAP1) [draw, circle, fill=uofgpillarbox, text=white] at (1,  0.6) { $P_1$ };
            \node (DFAP2) [draw, circle, fill=uofgpillarbox, text=white] at (2,  0.6) { $P_2$ };
            \node (DFAS1) [draw, circle, fill=uofglawn]                  at (1, -0.6) { $S_1$ };
            \node (DFAS2) [draw, circle, fill=uofglawn]                  at (2, -0.6) { $S_2$ };

            \draw [->, >=latex, thick]  (DFAI)  to (DFAP1);
            \draw [->, >=latex, thick]  (DFAI)  to (DFAS1);
            \draw [->, >=latex, thick]  (DFAP1) to (DFAP2);
            \draw [<->, >=latex, thick] (DFAP1) to (DFAS1);
            \draw [->, >=latex, thick]  (DFAS1) to (DFAS2);
            \draw [->, >=latex, thick]  (DFAP2) to (DFAS1);
            \draw [->, >=latex, thick]  (DFAS2) to (DFAP1);
        \end{scope}

        \begin{scope}
            \node [anchor=north west] at (7.5, 0.3) {
                \begin{minipage}{4.5cm}
                    \centering
                    \setlength{\tabcolsep}{3pt}
                    \begin{tabular}{cccc}
                        \toprule
                        Flight & \multicolumn{3}{c}{Matches} \\[2pt] \midrule
                        0 & (0,6) & (3,2) & (5,4) \\
                        1 & (0,2) & (4,1) & (6,5) \\
                        2 & (2,1) & (5,0) & (6,3) \\
                        3 & (1,5) & (3,0) & (4,6) \\
                        4 & (3,5) & (6,1) & (2,4) \\
                        5 & (1,3) & (0,4) & (5,2) \\
                        6 & (4,3) & (2,6) & (1,0) \\ \bottomrule
                    \end{tabular}
                \end{minipage}
            };
        \end{scope}

    \end{tikzpicture}
    \caption{A pictorial representation of the orientation process, stage 4. Top right is the actual
        oriented schedule. Below that is the DFA to satisfy criterion~5. On the left is the zero/one
        variables, a row representing a skipper's sequence of competitors. An edge between variables
        corresponds to a matched pair, that must take different values.}\label{oriented}
\end{figure}

@@

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.48\textwidth}
    \centering
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (5,2) & (4,3) & (1,6) \\
        1 & (4,2)  & (6,5) & (3,1) \\
        2 & (6,4) & (2,1) & (3,5) \\
        3 & (6,2) & (5,0) & (1,7) \\
        4 & (5,1) & (0,6) & (2,7) \\
        5 & (7,5) & (2,0) & (6,3) \\
        6 & (0,7) & (4,1) & (3,2) \\
       7 & (7,4)  & (0,3) &  \\
       8 & (4,0)  & (7,3) &  \\
       9 & (5,4)  & (7,6) & (1,0) \\ \bottomrule
    \end{tabular}
\label{08-06a}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (2,7) & (3,0) & (5,4) \\
        1 & (0,2)  & (4,3) & (7,5) \\
        2 & (0,4) & (7,6) & (5,3) \\
        3 & (4,6) & (5,0) & (3,1) \\
        4 & (6,5) & (3,2) & (1,4) \\
        5 & (6,3) & (4,7) & (2,1) \\
        6 & (7,3) & (1,6) & (4,2) \\
       7 & (7,1)  & (2,5) & (6,0) \\
       8 & (5,1)  & (0,7) & (6,2) \\
       9 & (1,0)  & & \\ \bottomrule
    \end{tabular}
\label{08-06b}
\end{minipage}
\caption{Schedules for 8 skippers and 6 boats. On the left, the published ISAF schedule (illegal),
and on the right is our schedule.}
\label{08-06}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.48\textwidth}
\centering
\begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (0,7) & (3,2) & (5,4) \\
        1 & (0,2) & (7,4) & (5,3) \\
        2 & (4,0) & (7,3) & (2,5) \\
        3 & (3,0) & (2,4) & (6,5) \\
        4 & (4,3) & (5,1) & (8,6) \\
        5 & (3,1) & (6,2) & (4,8) \\
        6 & (6,3) & (1,4) & (8,2) \\
        7 & (4,6) & (2,7) & (1,8) \\
        8 & (7,6) & (0,8) & (2,1) \\
        9 & (8,7) & (5,0) & (6,1) \\
        10 & (8,5) & (1,7) & (0,6) \\
        11 & (7,5) & (3,8) & (1,0) \\ \bottomrule
    \end{tabular}
\centering
\label{09-06}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\centering
\begin{tabular}{ccccc}
        \toprule
        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
        0 & (0,6) & (3,2) & (5,4) & (1,7) \\
        1 & (2,0) & (6,3) & (4,1) & (8,7) \\
        2 & (6,4) & (0,5) & (7,2) & (3,8) \\
        3 & (4,7) & (1,8) & (0,3) & (5,2) \\
        4 & (3,1) & (7,5) & (8,0) & (2,6) \\
        5 & (3,7) & (4,8) & (2,1) & (6,5) \\
        6 & (8,2) & (1,6) & (5,3) & (0,4) \\
        7 & (5,1) & (7,0) & (6,8) & (4,3) \\
        8 & (8,5) & (2,4) & (7,6) & (1,0) \\ \bottomrule
        & & & & \\
        & & & & \\
        & & & & \\
    \end{tabular}
\label{09-08}
\end{minipage}
\caption{Two new schedules. On the left, 9 skippers and 6 boats, and on the right 9 skippers and 8 boats.}
\label{09}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[h]
\begin{minipage}[t]{0.48\textwidth}
    \centering
\begin{tabular}{cccc}
 \toprule
Flight & \multicolumn{3}{c}{Matches} \\ \midrule
0 & (8,3) &  (1,7) &  (0,9) \\
1 & (7,3) &  (0,8) &  (1,9) \\
2 & (0,7) &  (9,3) &  (1,8) \\
3 & (6,2) &  (5,0) &  (7,4) \\
4 & (5,2) &  (6,4) &  (3,0) \\
5 & (8,6) &  (2,9) &  (4,1) \\
6 & (7,2) &  (4,8) &  (9,6) \\
7 & (2,4) &  (0,6) &  (7,5) \\
8 & (6,1) &  (5,9) &  (8,2) \\
9 & (9,4) &  (8,7) &  (6,5) \\
10 & (9,7) &  (6,3) &  (8,5) \\
11 & (7,6) &  (3,1) &  (9,8) \\
12 & (4,3) &  (5,1) &  (2,0) \\
13 & (3,5) &  (4,0) &  (2,1) \\
14 & (5,4) &  (3,2) &  (1,0) \\ \bottomrule
\end{tabular}
\label{10-06a}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\centering
\begin{tabular}{ccccc}
\toprule
Flight & \multicolumn{3}{c}{Matches} \\ \midrule
0 & (4,7) & (3,2) & (0,5) \\
1 & (2,4) & (7,0) & (3,5) \\
2 & (0,4) & (7,3) & (5,2) \\
3 & (4,3) & (0,2) & (5,7) \\
4 & (3,0) & (6,5) & (2,7) \\
5 & (6,3) & (7,1) & (8,2) \\
6 & (7,6) & (2,1) & (9,8) \\
7 & (2,6) & (8,7) & (4,9) \\
8 & (6,8) & (1,4) & (7,9) \\
9 & (8,1) & (5,4) & (9,6) \\
10 & (5,1) & (9,2) & (4,6) \\
11 & (1,9) & (6,0) & (8,4) \\
12 & (0,9) & (3,8) & (6,1) \\
13 & (8,0) & (9,5) & (1,3) \\
14 & (5,8) & (9,3) & (1,0) \\ \bottomrule
\end{tabular}
\label{10-06b}
\end{minipage}
\caption{Schedules for 10 skippers and 6 boats. On the left, the ISAF published schedule (illegal),
and on the right, our schedule.}
\label{10-06}
\end{figure}
\end{center}
